### 2020-04-21 discussion.tex
Improved the discussion section.

\fix{A short summary of the observations in this paper to facilitate the discussion below.}

@@

In Titan, the mitigation component included replacing about 11,000 GPUs and
changing the job scheduling strategy~\cite{8665764}. Replacing about 59\% of
Titan's 18,688 GPUs helped to improve productivity by restoring some of the lost
capability, but it was a costly and time-consuming effort. Changing the job
scheduling strategy to run larger jobs on more reliable and smaller jobs on less
reliable nodes played a crucial role in maintaining productivity at reduced
capability.

The options of replacing failed components and employing reliability-aware
resource management may not be available or cost effective for other
supercomputing centers dealing with similar unexpected reliability issues in
their systems. Replacement components may not be readily available and may have
to be manufactured, which can be impossible for technology that is no longer
supported by the original manufacturer. There is also a financial aspect, such
as service contract and/or warranty expiration and the operational budget of a
supercomputing center not having significant funds for replacement costs. There
is also the time and financial cost for root-cause analysis and developing a
hardware and software mitigation strategy in the first place. Reliability-aware
resource scheduling also has its limitations, as the network architecture needs
to be taken into account. Titan's 3D torus network creates certainly more
challenges for efficient job allocations, than the fat tree network of Titan's
successor, Summit~\cite{olcf:summit}. Nodes associated with the same job need to
be close to each other on the network for performance. Alternatively, partially
or completely replacing the aging and failing supercomputer with a new system,
even if this solution offers less capability, may be more cost effective in the
end.

Other mitigation components for Titan included matching the checkpointing
interval of applications with the system's current
reliability~\cite{bautista-gomez16reducing, 6903564}. The experienced issue here
was the lack of automated communication of system reliability information and
the lack of flexibility in application-level checkpoint/restart implementations.
Constantly measuring and reporting current system reliability is not an automated
real-time task in currently deployed supercomputers. Applications are typically
not designed to skip a checkpoint when system reliability is good or take more
frequent checkpoints when system reliability is getting worse.

@@

\fix{\begin{itemize}
\item Cray and NVIDIA take care of the hardware and some systems and driver
  software so moving and troubleshooting hardware is their cost.
\item Checkpoint strategies, allocation strategies, job resource
  management, are all under OLCF control. What can OLCF do/change to
  mitigate fallout in terms of delivering computing to customers when
  facing machine disasters like the two episodes (2013 and 2016) on Titan?
\end{itemize}}

\fix{RA: Recommendation for system operators if they see similar 
wide-spread failures in their system well before the expected lifetime 
of the machine. Should they replace all components or just partially
upgrade the machine. Tradeoff?}

>>>>

\fix{Possibly a short summary of the observations in this paper to facilitate the discussion below.}

@@

%%%%%%%%%%%%
% Mitigation
%%%%%%%%%%%%
\subsection{Mitigation}
\label{section:mitigation}

In Titan, the mitigation component included replacing about 11,000 GPUs and
changing the job scheduling strategy~\cite{8665764}. Replacing about 59\% of
Titan's 18,688 GPUs helped to improve productivity by restoring some of the lost
capability, but it was a costly and time-consuming effort. Changing the job
scheduling strategy to run larger jobs on more reliable and smaller jobs on less
reliable nodes played a crucial role in maintaining productivity at reduced
capability. However, jobs running on larger portions of the system, utilizing
most or all of its resources, were still impacted by the failing GPUs and
corresponding low system MTBF.

The options of replacing failed components and employing reliability-aware
resource management may not be available or cost effective for other
supercomputing centers dealing with similar unexpected reliability issues.
%
Replacement components may not be readily available and may have to be
manufactured, which can be impossible for technology that is no longer supported
by the original manufacturer. Experienced errors or failures may be caused by
software, which can be difficult to fix if the software itself or the deployed
version is no longer supported by the vendor.

There is also a financial aspect, such as service contract and/or warranty
expiration and the operational budget of a supercomputing center not having
significant funds for replacement/reengineering costs or a manufacturer or
vendor not paying for them.
%
There is additionally the time and financial cost for root-cause analysis and
developing a hardware and/or software mitigation strategy in the first place.
Fixing a problem requires finding and understanding it, which can be difficult 
in today's complex systems and may require knowledge that only the original 
manufacturer or vendor possesses.

Reliability-aware resource scheduling also has its limitations, as the network
architecture needs to be taken into account. Titan's 3D torus network creates
certainly more challenges for efficient job allocations, than the fat tree
network of Titan's successor, Summit~\cite{olcf:summit}. Nodes associated with
the same job need to be close to each other on the network for maximum
application performance.
%
Alternatively, partially or completely replacing the aging and failing
supercomputer with a new system, even if this solution offers less capability,
may be more cost effective in the end.

Other mitigation components for Titan included matching the checkpointing
interval of applications with the system's current
reliability~\cite{bautista-gomez16reducing, 6903564}. The experienced issue here
was the lack of automated communication of system reliability information and
the lack of flexibility in application-level checkpoint/restart implementations.
Constantly measuring and reporting current system reliability is not an automated
real-time task in many currently deployed supercomputers. Applications are
typically not designed to skip a checkpoint when system reliability is good or
take more frequent checkpoints when system reliability is getting worse.

%%%%%%%%%%%%%%%%%%%%
% Long-term Planning
%%%%%%%%%%%%%%%%%%%%
\subsection{Long-term Planning}
\label{section:planning}

@@

Supercomputer center policies regarding reliability monitoring, resource
allocation and checkpointing strategies need to be powerful and flexible enough
to facilitate mitigation for such unexpected reliability threats. System
acquisition contracts may need to include performance requirements for degraded
operation, such as a 60\% performance capability if the MTBF drops by a
magnitude.
